Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-03-30 RMS/submission.tex
finished the final version of revision 1

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{mathabx}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

@@

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{P}{eriodic} task scheduling is one of the most important
topics within the field of industrial real-time systems.
%due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
A set of periodic tasks is said to be \emph{schedulable} with respect
to some scheduling algorithm if all jobs meet their
deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
\emph{fixed} priority scheduling algorithm for preemptive hard
real-time environments proposed by Liu and
Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
jobs according to the periods of the corresponding tasks: the smaller
period, the higher priority. RMS is proven to be the \emph{optimal}
fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
in the sense that any set of tasks, which is schedulable under
\emph{some} fixed priority scheduling algorithm, is also schedulable
with respect to RMS. It is widely used in safety-critical real-time
applications, such as vehicles and avionics, thanks to its optimality
and easiness to implement.

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
TR)$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \emph{Terms} are expressions built from function symbols and
  variables.
\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of \emph{conditional equations} and
  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
  such as associativity, commutativity and identity.  $(\Sigma, E\cup
  A)$ models the system's ``static'' states as terms of some sort, and
  is equipped with a built-in specification of a sort \verb|Time|.
\item $IR$ is a set of \emph{labeled conditional rewrite rules}
  specifying the system's local transitions. Each rule has the form
  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
  \emph{label}, $t,t'$ are terms. Such a rule specifies an
  \emph{instantaneous transition}, without consuming time, from an
  instance of $t$ to the corresponding instance of $t'$,
  \emph{provided} the conditions hold.
\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }r\mbox{
  \textbf{if} }cond$ that specify \emph{timed transitions}, which
  advances time by $r$ time units in the \emph{entire} state modeled
  by term $s$. $IR$ and $TR$ together model the ``dynamic'' behaviors
  of the system.
\end{itemize}

In rewriting logic, rewrite rules are applied non-deterministically,
that is, when several rules can be applied on a given term $t$, any of
them may be chosen. Hence non-deterministic behaviors can be modeled
naturally in Real-Time Maude.  Real-Time Maude also supports
specifications in \emph{object-oriented} style.  A class declaration
$\texttt{class }C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
defines a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
to $s_n$, respectively. An \emph{object} of class $C$ is represented
as a term $\texttt{< } O\texttt{:} C \texttt{ | }
att_1\texttt{:}val_1\texttt{,} \ldots
\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. Rules
can be defined on a given class. A \emph{subclass} inherits all the
attributes and rules of its superclasses.

@@

\section{Formal Modeling of the Implementation}
\label{s:formalism}
Considering some technical details of the platform, such as interrupt
mask mechanism, we model the implementation under the following
assumptions:

@@

We have analyzed our model in ten different scenarios, including both
realistic ones provided by our industrial partner and experimental
ones designed by ourselves, four of them are described below:
\begin{itemize}
\item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
  $C_1=3ms$, $T_2=25ms$ and $C_2=7ms$.
\item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
  $C_1=2ms$, $T_2=25ms$ and $C_2=2.3ms$.
\item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$ and
  $C_3=3ms$.
\item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$, $T_3=15ms$ and
$C_3=4.5ms$.
\end{itemize}
Note that thanks to the powerful expressiveness of Real-Time Maude, we
only need to define an initial state of sort \verb|System| to specify
a given task set. No necessity to modify the model is needed.

@@

The results above have demonstrated that our approach is capable of
handling realistic industrial systems. However to further exam the
efficiency of our approach, we also apply our method to larger test
scenarios. Test scenarios are generated randomly. We verify the
schedulability of them under the above setting on an Intel Core 2 Quad
Q9550, 2.83GHz, 4-cores machine with 8GB RAM running 64-bit Ubuntu
15.04. Among the 50 generated test scenarios with 5 tasks, we find
that the execution time of the model checking command for each
scenario varies from about $300ms$ up to a timeout, which is set to
$90$ minutes. This is because the efficiency of model checking depends
on the scale of the state space. And the scale is further positively
correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
is the number of periodic tasks. By the generated test scenarios, it
turns out that the model checking command for schedulability in our
model is able to handle scenarios, where $mn$ is up to about $10^6$,
in an acceptable period of time say $90$ minutes.

@@

In general, completeness of untimed model checking cannot be achieved
for any systems, any time sampling strategies and any
properties. However, \"Olveczky and Meseguer proved the completeness
of untimed temporal logic model checking, under the maximal time
sampling strategy, for a large class of real-time systems possessing a
set of ``good'' properties that is called \emph{time-robustness}, and
for a set of ``good'' LTL formulae constructed by
\emph{tick-invariant} propositions\footnote{We avoid introducing the
  definitions of time-robustness and tick-invariance, due to the
  requirements of extra rewriting logic
  background.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:
\begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
\label{t:completeness}
Given a time-robust real-time rewrite theory $\cal R$, a set $AP$ of
tick-invariant atomic propositions, an LTL formula $\Phi$ (excluding
the \emph{next} operator $\bigcirc$) whose atomic propositions are
contained in $AP$. The untimed temporal logic model checking verifying
$\Phi$ is \emph{complete} under the maximal time sampling strategy.
\end{theorem}

Therefore, we achieve the following theorem, showing that the results
in Section~\ref{ss:results} are complete.
\begin{theorem}
\label{t:main}
Our approach using untimed model checking to verify the schedulability
and the correctness of our model is complete.
\end{theorem}
\begin{IEEEproof}
By showing that our model is time-robust and that the two defined
atomic propositions--\verb|taskTimeout| and \verb|correct|--are
tick-invariant, then using Theorem~\ref{t:completeness}. For a more
detailed proof, see the Appendix.
\end{IEEEproof}

@@

Considering schedulability test, Liu and
Layland~\cite{DBLP:journals/jacm/LiuL73} gave the famous sufficient
condition that a set of periodic tasks is schedulable with respect to
RMS if $\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$
holds. Then a more sufficient condition, known as \emph{Hyperbolic
  Bound}, which has the same complexity as Liu and Layland's, was
proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
necessary and sufficient conditions for schedulability were derived
independently in~\cite{DBLP:journals/rts/SpruntSL89}
and~\cite{audsley1993deadline}, requiring more sophisticated analysis
on the task set. Nevertheless, all these results take no overhead into
account, being not as realistic as ours. Katcher et al. did consider
overhead in their schedulability analysis, under several models based
on different kinds of popular
implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
target implementation is not in their scope. Furthermore, compared
with those theoretical analyses, our approach based on formal modeling
and verification has three advantages. One is that if our
schedulability test answers ``no'', it returns at the same time a real
counterexample, which is able to guide our engineer to adjust the
design, by changing either the priorities or even the scheduling
algorithm. The second is that, when a fresh scheduling strategy is
applied, our analysis can be adjusted only by modifying the model,
while theoretical approaches may need thorough analyses and reasoning.
The last one is that, considering overhead and details of hardware do
introduce some kind of non-determinism into the model. For example, in
our model, if the running task is complete \emph{right} at the time
when an interrupt request occurs, two different behaviors are
possible: (i) the system performs task switching, during which the
interrupt request is masked, hence the scheduling and initiation of
tasks may be delayed; (ii) the system answers the interrupt request
immediately, the switching being delayed. Tackling such
non-determinism via theoretical analyses seems more complicated than
our automatic approach.

\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} also made use of
model checking to analyze the RMS algorithm along the same line but
with different languages and tools. The RMS algorithm is investigated
using an extension of SPIN~\cite{DBLP:journals/tse/Holzmann97}
in~\cite{TianD2011}, while the logic programming language
TMSVL~\cite{DBLP:conf/icfem/HanDW12} and its model checker are applied
in~\cite{DBLP:conf/iceccs/CuiDT14}. The work presented
in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} has two main
differences with ours. The first one, which is also the motivational
one, is that they considered only the ideal setting of the algorithm
as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an implementation
which contains much more complex details. In fact, our model of the
implementation can easily degenerate to a model of the RMS algorithm,
if we let the times for scheduling and switching be zero. The other
difference is that when adding a new task into the task set, the
models in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} should
be modified by explicitly defining a sub-model of the new task and its
behaviors. In particular, the scheduling part of the model
in~\cite{TianD2011} needs adjustments as well to include a new
task. Nevertheless, a new task set is specified in our approach merely
by giving a new initial state, without necessity to modify the model,
as already emphasized in Section~\ref{ss:results}. On the other hand,
\cite{TianD2011} used a discrete time domain in the model, while we
employ a generic time domain, which is flexible to be instantiated on
either discrete or dense ones. In~\cite{DBLP:conf/iceccs/CuiDT14}, the
time domain is dense, and a modeling strategy like our maximal time
sampling strategy is applied to reduce the state space. However, a
completeness statement like Theorem~\ref{t:main} was not given
in~\cite{DBLP:conf/iceccs/CuiDT14}.

@@

\appendix[Proof of Theorem~\ref{t:main}]
\label{a:proof}
\setcounter{theorem}{0}
\renewcommand{\thetheorem}{\thesection.\arabic{theorem}}
\newcommand{\lrps}[2]{\rightarrow^{#1}_{#2}}

>>>>

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{mathabx}

% for highlighting
\usepackage{color,soul}
\soulregister\cite7
\soulregister\ref7
\soulregister\pageref7

\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

@@

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{P}{eriodic} task scheduling is one of the most important
topics within the field of industrial real-time systems.
%due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
{A set of periodic tasks is said to be \emph{schedulable} with respect
to some scheduling algorithm if all jobs meet their
deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
\emph{fixed} priority scheduling algorithm for preemptive hard
real-time environments proposed by Liu and
Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
jobs according to the periods of the corresponding tasks: the smaller
period, the higher priority. RMS is proven to be the \emph{optimal}
fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
in the sense that any set of tasks, which is schedulable under
\emph{some} fixed priority scheduling algorithm, is also schedulable
with respect to RMS. It is widely used in safety-critical real-time
applications, such as vehicles and avionics, thanks to its optimality
and easiness to implement.

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
TR)$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \hl{\emph{Terms} are expressions built from function symbols and
  variables.}
\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of \emph{conditional equations} and
  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
  such as associativity, commutativity and identity.  $(\Sigma, E\cup
  A)$ models the system's ``static'' states \hl{as terms of some sort}, and
  is equipped with a built-in specification of a sort \verb|Time|.
\item $IR$ is a set of \emph{labeled conditional rewrite rules}
  specifying the system's local transitions. Each rule has the form
  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
  \emph{label}, \hl{$t,t'$ are terms}. Such a rule specifies an
  \emph{instantaneous transition}, without consuming time, from an
  instance of $t$ to the corresponding instance of $t'$,
  \emph{provided} the conditions hold.
\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }r\mbox{
  \textbf{if} }cond$ that specify \emph{timed transitions}, which
  advances time by $r$ time units in the \emph{entire} state modeled
  by term $s$. $IR$ and $TR$ together model the ``dynamic'' behaviors
  of the system.
\end{itemize}

In rewriting logic, rewrite rules are applied non-deterministically,
that is, when several rules can be applied on a given term $t$, any of
them may be chosen. Hence non-deterministic behaviors can be modeled
naturally in Real-Time Maude.  Real-Time Maude also supports
specifications in \emph{object-oriented} style.  A class declaration
$\texttt{class }C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
defines a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
to $s_n$, respectively. An \emph{object} of class $C$ is represented
as a term $\texttt{< } O\texttt{:} C \texttt{ | }
att_1\texttt{:}val_1\texttt{,} \ldots
\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. \hl{Rules
can be defined on a given class.} A \emph{subclass} inherits all the
attributes and rules of its superclasses.

@@

\section{\hl{Formal Modeling of the Implementation}}
\label{s:formalism}
Considering some technical details of the platform, such as interrupt
mask mechanism, we model the implementation under the following
assumptions:

@@

We have analyzed our model in ten different scenarios, including both
realistic ones provided by our industrial partner and experimental
ones designed by ourselves, four of them are described below:
\begin{itemize}
\item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
  $C_1=3ms$, $T_2=25ms$ and $C_2=7ms$.
\item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
  $C_1=2ms$, $T_2=25ms$ and $C_2=2.3ms$.
\item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$ and
  $C_3=3ms$.
\item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$, $T_3=15ms$ and
$C_3=4.5ms$.
\end{itemize}
\hl{Note that thanks to the powerful expressiveness of Real-Time Maude, we
only need to define an initial state of sort} \verb|System| \hl{to specify
a given task set. No necessity to modify the model is needed.}

@@

\hl{The results above have demonstrated that our approach is capable of
handling realistic industrial systems. However to further exam the
efficiency of our approach, we also apply our method to larger test
scenarios. Test scenarios are generated randomly. We verify the
schedulability of them under the above setting on an Intel Core 2 Quad
Q9550, 2.83GHz, 4-cores machine with 8GB RAM running 64-bit Ubuntu
15.04. Among the 50 generated test scenarios with 5 tasks, we find
that the execution time of the model checking command for each
scenario varies from about $300ms$ up to a timeout, which is set to
$90$ minutes. This is because the efficiency of model checking depends
on the scale of the state space. And the scale is further positively
correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
is the number of periodic tasks. By the generated test scenarios, it
turns out that the model checking command for schedulability in our
model is able to handle scenarios, where $mn$ is up to about $10^6$,
in an acceptable period of time say $90$ minutes.}

@@

In general, completeness of untimed model checking cannot be achieved
for any systems, any time sampling strategies and any
properties. However, \"Olveczky and Meseguer proved the completeness
of untimed temporal logic model checking, under the maximal time
sampling strategy, \hl{for a large class of real-time systems possessing a
set of ``good'' properties that is called \emph{time-robustness}, and
for a set of ``good'' LTL formulae constructed by
\emph{tick-invariant} propositions\footnote{We avoid introducing the
  definitions of time-robustness and tick-invariance, due to the
  requirements of extra rewriting logic
  background.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:}
\begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
\label{t:completeness}
Given a time-robust real-time rewrite theory $\cal R$, a set $AP$ of
tick-invariant atomic propositions, an LTL formula $\Phi$ (excluding
the \emph{next} operator $\bigcirc$) whose atomic propositions are
contained in $AP$. The untimed temporal logic model checking verifying
$\Phi$ is \emph{complete} under the maximal time sampling strategy.
\end{theorem}

Therefore, we achieve the following theorem, showing that the results
in Section~\ref{ss:results} are complete.
\begin{theorem}
\label{t:main}
Our approach using untimed model checking to verify the schedulability
and the correctness of our model is complete.
\end{theorem}
\begin{IEEEproof}
By showing that our model is time-robust and that the two defined
atomic propositions--\verb|taskTimeout| and \verb|correct|--are
tick-invariant, then using Theorem~\ref{t:completeness}. \hl{For a more
detailed proof, see the Appendix.}
\end{IEEEproof}

@@

Considering schedulability test, Liu and
Layland~\cite{DBLP:journals/jacm/LiuL73} gave the famous sufficient
condition that a set of periodic tasks is schedulable with respect to
RMS if $\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$
holds. Then a more sufficient condition, known as \emph{Hyperbolic
  Bound}, which has the same complexity as Liu and Layland's, was
proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
necessary and sufficient conditions for schedulability were derived
independently in~\cite{DBLP:journals/rts/SpruntSL89}
and~\cite{audsley1993deadline}, requiring more sophisticated analysis
on the task set. Nevertheless, all these results take no overhead into
account, being not as realistic as ours. Katcher et al. did consider
overhead in their schedulability analysis, under several models based
on different kinds of popular
implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
target implementation is not in their scope. \hl{Furthermore, compared
with those theoretical analyses, our approach based on formal modeling
and verification has three advantages. One is that if our
schedulability test answers ``no'', it returns at the same time a real
counterexample, which is able to guide our engineer to adjust the
design, by changing either the priorities or even the scheduling
algorithm. The second is that, when a fresh scheduling strategy is
applied, our analysis can be adjusted only by modifying the model,
while theoretical approaches may need thorough analyses and reasoning.
The last one is that, considering overhead and details of hardware do
introduce some kind of non-determinism into the model. For example, in
our model, if the running task is complete \emph{right} at the time
when an interrupt request occurs, two different behaviors are
possible: (i) the system performs task switching, during which the
interrupt request is masked, hence the scheduling and initiation of
tasks may be delayed; (ii) the system answers the interrupt request
immediately, the switching being delayed. Tackling such
non-determinism via theoretical analyses seems more complicated than
our automatic approach.}

\hl{\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} also made use of
model checking to analyze the RMS algorithm along the same line but
with different languages and tools. The RMS algorithm is investigated
using an extension of SPIN~\cite{DBLP:journals/tse/Holzmann97}
in~\cite{TianD2011}, while the logic programming language
TMSVL~\cite{DBLP:conf/icfem/HanDW12} and its model checker are applied
in~\cite{DBLP:conf/iceccs/CuiDT14}. The work presented
in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} has two main
differences with ours. The first one, which is also the motivational
one, is that they considered only the ideal setting of the algorithm
as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an implementation
which contains much more complex details. In fact, our model of the
implementation can easily degenerate to a model of the RMS algorithm,
if we let the times for scheduling and switching be zero. The other
difference is that when adding a new task into the task set, the
models in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} should
be modified by explicitly defining a sub-model of the new task and its
behaviors. In particular, the scheduling part of the model
in~\cite{TianD2011} needs adjustments as well to include a new
task. Nevertheless, a new task set is specified in our approach merely
by giving a new initial state, without necessity to modify the model,
as already emphasized in Section~\ref{ss:results}. On the other hand,
\cite{TianD2011} used a discrete time domain in the model, while we
employ a generic time domain, which is flexible to be instantiated on
either discrete or dense ones. In~\cite{DBLP:conf/iceccs/CuiDT14}, the
time domain is dense, and a modeling strategy like our maximal time
sampling strategy is applied to reduce the state space. However, a
completeness statement like Theorem~\ref{t:main} was not given
in~\cite{DBLP:conf/iceccs/CuiDT14}.}

@@

\appendix[\hl{Proof of Theorem~\ref{t:main}}]
\label{a:proof}
\setcounter{theorem}{0}
\renewcommand{\thetheorem}{\thesection.\arabic{theorem}}
\newcommand{\lrps}[2]{\rightarrow^{#1}_{#2}}
